\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
author: properly add new line

\author[*]{\large
{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
\author[*]{\large
{\bf Che-Kang Wu}\thanks{an4006048$@$mail.ncku.edu.tw}}
\author[**]{\large
{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
\affil[*]{Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\affil[**]{Department of Electrical and Electronic Engineering, \\
National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)}
\date{}

>>>>

\author[*]{\large
{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
\author[*]{\large
{\bf Che-Kang Wu}\thanks{an4006048$@$mail.ncku.edu.tw}}
\author[**]{\large
{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
\affil[*]{Department of Computer Science and Information Engineering,
\newline
National Cheng Kung University, Taiwan
\newline
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\affil[**]{Department of Electrical and Electronic Engineering,
\newline
National Taiwan University
\newline
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)}
\date{}
